Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-09-15 notes/notes.tex
inserted new plot into the notes, corrected some errors in the latex file like xelatex shebang and location of figures
enhanced the discussion on the broadening

% !TEX TS-program = xelatex
\documentclass[12pt]{article}
\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec,color}
\usepackage[margin=0.5in,bottom=0.6in]{geometry}
\graphicspath{{./figures/}}
\usepackage[T1]{fontenc}
\usepackage[pdfusetitle]{hyperref}
\renewcommand{\arraystretch}{2}
\setlength\delimitershortfall{-2pt}
\setcounter{tocdepth}{1}
\DeclareMathOperator{\sech}{sech}
\raggedbottom
\numberwithin{equation}{section}
\allowdisplaybreaks

@@

\section{Spectral function of the single-impurity Anderson model}
To get a better look at what we are getting into and what we should expect going forward, we first calculate the spectral function of the smaller single-impurity Anderson model that is obtained as the low-energy Hamiltonian of an URG analysis of the full SIAM. This ow energy effective Hamiltonian is
\begin{equation}\begin{aligned}
	\epsilon_d \hat n_d + U\hat n_{d \uparrow} \hat n_{d \downarrow} + v \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + \sum_{k \in \left[-\Lambda^*, \Lambda^*\right], \sigma}\epsilon_k \hat n_{k\sigma}
\end{aligned}\end{equation}
All the impurity couplings are fixed point values, and the momentum states of the bath now run over a reduced bandwidth. The subscript \(d\) indicates that the operator is that of the impurity, while the subscript \(0\) indicates it is of the zeroth site of the bath: \(c_0 = \frac{1}{\sqrt N}\sum_k c_k\). The spectral function of the SIAM is already known from other methods like the numerical renormalization group. For small values of \(U\), the spectral function consists of just the central quasiparticle excitation peak. At larger values of \(U\), we see the emergence of the two Hubbard side bands while the spectral weight at the centre decreases. We also calculated the spectral function of the low energy theory sing exact diagonalization. The plots are shown in fig.~\ref{siam_spec_func}.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.9\textwidth]{./siam_specfunc_all.pdf}
	\caption{Spectral function of the effective SIAM Hamiltonian for various values of \(\frac{U}{\Delta}\). \(\Delta\) is defined by the height of the central peak in the non-interacting model \(U=0\). The inset shows a zoom-in of the final spectral function \(\left( \frac{U}{\Delta} = 19.71 \right)\) near \(\omega = 0\).}
	\label{siam_spec_func}
\end{figure}
\\\\
Because we kept only a discrete bath of 4 momentum states, \textit{we had to artificially enforce the constancy of the height of the central peak.} To convert the delta functions into a continuous spectrum, we  The central peak (or equivalently, the central pole in the impurity Greens function) does not vanish even for exhorbitantly large values of \(\frac{U}{\Delta}\), implying that there is no stable local moment phase in the SIAM (a local moment phase would involve a gap at zero frequency in the impurity spectral function). Formally, the local moment phase will be stable only at \(U \to \infty\) or \(v^* = 0\).
\\\\
We also checked how the width of the central peak varies with increasing \(U\). The behaviour is shown in fig.~\ref{fwhm}. The width was also fitted against a function, as shown in the plot.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.6\textwidth]{./width_vs_U_simple_fit.pdf}
	\caption{The decay of the full width at half maximum (FWHM) of the central peak, with increasing \(\frac{U}{\Delta}\). The behaviour satisfies a function of the form shown in the legend.}
	\label{fwhm}
\end{figure}

>>>>

\documentclass{article}
\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec,color}
\usepackage[margin=0.5in,bottom=0.6in]{geometry}
\graphicspath{{../figures/}}
\usepackage[T1]{fontenc}
\usepackage[pdfusetitle]{hyperref}
\renewcommand{\arraystretch}{2}
\setlength\delimitershortfall{-2pt}
\setcounter{tocdepth}{1}
\DeclareMathOperator{\sech}{sech}
\raggedbottom
\numberwithin{equation}{section}
\allowdisplaybreaks

@@

\section{Spectral function of the single-impurity Anderson model}
To get a better look at what we are getting into and what we should expect going forward, we first calculate the spectral function of the smaller single-impurity Anderson model that is obtained as the low-energy Hamiltonian of an URG analysis of the full SIAM. This ow energy effective Hamiltonian is
\begin{equation}\begin{aligned}
	\epsilon_d \hat n_d + U\hat n_{d \uparrow} \hat n_{d \downarrow} + v \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + \sum_{k \in \left[-\Lambda^*, \Lambda^*\right], \sigma}\epsilon_k \hat n_{k\sigma}
\end{aligned}\end{equation}
All the impurity couplings are fixed point values, and the momentum states of the bath now run over a reduced bandwidth. The subscript \(d\) indicates that the operator is that of the impurity, while the subscript \(0\) indicates it is of the zeroth site of the bath: \(c_0 = \frac{1}{\sqrt N}\sum_k c_k\). The spectral function of the SIAM is already known from other methods like the numerical renormalization group. For small values of \(U\), the spectral function consists of just the central quasiparticle excitation peak. At larger values of \(U\), we see the emergence of the two Hubbard side bands while the spectral weight at the centre decreases. We also calculated the spectral function of the low energy theory sing exact diagonalization. The plots are shown in fig.~\ref{siam_spec_func}.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=\textwidth]{./siam_specfunc_all.pdf}
	\caption{Spectral function of the effective SIAM Hamiltonian for various values of \(\frac{U}{\Delta}\). \(\Delta\) is defined by the height of the central peak in the non-interacting model \(U=0\). The inset shows a zoom-in of the final spectral function \(\left( \frac{U}{\Delta} = 19.71 \right)\) near \(\omega = 0\).}
	\label{siam_spec_func}
\end{figure}
\\\\
Because we kept only a discrete bath of 4 momentum states, \textit{we had to artificially enforce the constancy of the height of the central peak, using \cite{Langreth}.} To convert the discrete sum of delta functions into a continuous spectrum, we broadened them using a Gaussian. Following \cite{bulla_costi_nrg}, we replace the delta-functions at \(\pm x_n \equiv \pm(E_n - E_0)\) by normalised Gaussian functions
\begin{equation}\begin{aligned}
	\delta(\omega \pm x_n) \to \frac{1}{\eta_n\sqrt \pi}e^{-\left(\frac{\omega \pm x_n}{\eta_n}\right)^2}
\end{aligned}\end{equation}
The parameter \(\eta_n\) determines the height and width of the Gaussian, and is chosen such that the higher energy poles are broader than the lower energy ones.
\begin{equation}\begin{aligned}
	\eta_n = 2\Delta + \frac{1}{2}|x_n| 
\end{aligned}\end{equation}
where \(\Delta = \frac{V^2}{t}\) is the relevant energy scale of the non-interacting problem and \(t\) is the tight-binding hopping parameter of the conduction bath.
\\\\
The central peak (or equivalently, the central pole in the impurity Greens function) does not vanish even for exhorbitantly large values of \(\frac{U}{\Delta}\), implying that there is no stable local moment phase in the SIAM (a local moment phase would involve a gap at zero frequency in the impurity spectral function). Formally, the local moment phase will be stable only at \(U \to \infty\) or \(v^* = 0\).
\\\\
We also checked how the width of the central peak varies with increasing \(U\). The behaviour is shown in fig.~\ref{fwhm}. The width was also fitted against a function, as shown in the plot.
\begin{figure}[htpb!]
	\centering
	\includegraphics[width=0.5\textwidth]{./width_vs_U_simple_fit.pdf}
	\caption{The decay of the full width at half maximum (FWHM) of the central peak, with increasing \(\frac{U}{\Delta}\). The behaviour satisfies a function of the form shown in the legend.}
	\label{fwhm}
\end{figure}
